\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-05-21 paper.qmd
Update the PBMC screen shots and added new video links

Screen shots of the **langevitour** of the PBMC3k data set, shows the model-in-data space, a video of the tour animation is available at (<https://youtu.be/Gnhh4hfsbbg>).
:::

@@

Screen shots of the **langevitour** of the PBMC3k data set, shows the model in high-D, a video of the tour animation is available at (<https://youtu.be/R0EroJcGbas>).
:::

>>>>

Screen shots of the **langevitour** of the PBMC3k data set, shows the model-in-data space, a video of the tour animation is available at (<https://youtu.be/VqqWuE0Jj6A>).
:::

@@

Screen shots of the **langevitour** of the PBMC3k data set, shows the model in high-D, a video of the tour animation is available at (<https://youtu.be/5Y1hE4i7N2k>).
:::

### 2024-05-21 paper.tex
Update the PBMC screen shots and added new video links

\caption{\label{fig-pbmc1_sc}Screen shots of the \textbf{langevitour} of
the PBMC3k data set, shows the model-in-data space, a video of the tour
animation is available at (\url{https://youtu.be/Gnhh4hfsbbg}).}

@@

\caption{\label{fig-pbmc2_sc}Screen shots of the \textbf{langevitour} of
the PBMC3k data set, shows the model in high-D, a video of the tour
animation is available at (\url{https://youtu.be/R0EroJcGbas}).}

>>>>

\caption{\label{fig-pbmc1_sc}Screen shots of the \textbf{langevitour} of
the PBMC3k data set, shows the model-in-data space, a video of the tour
animation is available at (\url{https://youtu.be/VqqWuE0Jj6A}).}

@@

\caption{\label{fig-pbmc2_sc}Screen shots of the \textbf{langevitour} of
the PBMC3k data set, shows the model in high-D, a video of the tour
animation is available at (\url{https://youtu.be/5Y1hE4i7N2k}).}
